Future challenges for Research Software Engineering

### 2025-05-06 future_challenges_for_RSEng.tex

\section{Aspects of this future}
It is difficult to structure the different aspects in describing the future. We decided to consider
\begin{itemize}
\item The evolution of the term RSE
\item How is education reshaped by the digital transformation
\item What will the impact of AI be to the work of RSEs?
\item Changes to the Academic Institutions
\item Ethics and social considerations
\item Impact of alternate career paths for RTPs (\emph{Research Technical Professional}s)
\end{itemize}

>>>>

\section{Aspects of this future}
It is difficult to structure the different aspects in describing the future. We decided to consider
\begin{itemize}
\item The evolution of the term RSE,
\item How education is reshaped by the digital transformation,
\item What the impact of AI to the work of RSEs will look like,
\item Changes to the Academic Institutions,
\item Ethics and social considerations,
\item Impact of alternate career paths for RTPs (\emph{Research Technical Professional}s).
\end{itemize}
